---
title: "sys.nframe()"
author: "jim"
date: 2020-07-23T21:13:14-05:00
---

```{r setup, eval = FALSE , include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(rmarkdown)
```

In prior post, used ls() to list objects in a environment.   Often the
environment is .global_env() but when a function is called it executes in its
own environment.


Here we see what happens when one function calls another and we examine 
sys.nframe()


### nframe:  index of current frame | takes no arguments

```{r wrapper_nframe}

parentls <- function() {
  cat("nframe = ", sys.nframe() , "\n")
}

{
cat("nframe = ", sys.nframe() , "\n")
parentls()
}
```

How many levels down ?  0=GlobalEnv, 1= 1 level
```{r nframe_levels}


f  <- function() {
  parentls()
}

{
cat("nframe = ", sys.nframe() , "\n")
parentls()
f()
}


```
  
### sys.parent() works opposite direction to nframe
```{r sys_parent}
sys.parent(n = 1)

# n=1 is parent, n=2 grandparent
f  <- function(n=NULL) {
  sys.parent(n)
}

f(0)
f(1)
f(2)


# To get environment of ancestor frame

# n=1 is parent, n=2 grandparetn
g  <- function(n=NULL) {
  sys.frame(sys.parent(n))}
}

g(1)
g(0)

```

### sys.frame() takes n, returns env

```{r sys_frame}
sys.frame()
sys.status()

f  <- function(){
  sys.status()
}
z  <- f()
z$sys.frames

### and this is parent env of frame one level down.
parent.env(z$sys.frames[[1]])
```

```{r}

a  <- function() {
  cat("nframe = ", sys.nframe() , "\n")
  b()
}

b   <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
  sys.status()
}

a()


```

### 2 environemtns for a function !
```{r two_env}
E1  <- new.env()
E1$x  <- 0

E2  <- new.env()
E2$x  <- 10


f  <- function() {
  print(x)
}
environment(f)  <- E2
f()


environment(f)  <- E1
f()

```



```{r more}



a  <- function() {
  cat("nframe = ", sys.nframe() , "\n")
  b()
}

b   <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
  c()
}

c  <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
}


cat("nframe = ", sys.nframe() , "\n")
a() # objects in a's environment

f  <- function() a()
f()
```
recursive!
sys.nframe()
blogdown has trouble  Cstack; 
```{r loop, eval=FALSE, include=FALSE   }
cat("nframe = ", sys.nframe() , "\n")
a  <- function() {
  if (sys.nframe() == 9) return()
  cat("nframe = ", sys.nframe() , "\n")
  a()
}
a()
```

```{r render, eval=FALSE  }
rmarkdown::render(
   "/home/jim/code/hugo_projects/blog/content/post/0001_nframe.Rmd", 
   output_format = "pdf_document",
   output_file= "~/Downloads/print_and_delete/out.pdf")
```


old
AAA Example:   objects in calling env() (or parent.frame())
https://stackoverflow.com/questions/28641395/what-is-parent-frame-of-r
```{r main}
# objects in parent.frame (calling env)
parentls <- function() {
  ls(envir = parent.frame())
}

a<-function() {
    x <- 5
    parentls()
}

b <- function() {
    z <- 10
    parentls()
 }

a() # objects in a's environment
b()
parentls()
```
