---
title: "parent.frame()"
author: "jim"
date: 2020-17-23T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, eval = FALSE , include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(jimTools)
library(blogdown)

knitr::knit_exit()
```

## Calling environment is found with base::parent.frame() 
  - parent.frame of R_GlobalEnv is itself

```{r simple}

parent.frame() 

f  <- function() print(parent.frame())  
f()  # also R_GlobalEnv

```

Calling env of g is env for f
```{r not_global}

g  <- function() print(parent.frame())

f <- function() g()
f()
```


Repeat, also find the frames, env
-   
-  Global takes value 0
-  f , one level down, takes 1
-  g,  two levels down, takes 2
-  environment(), active env
-  environment(h), env where h is defined
-  parent.frame(), calling env

```{r nframe_adv}

g  <- function() {
  cat("g:  nframe = ", sys.nframe() , "\n")
  cat("g def env:  ")
  print(environment(g))  # g is defined in Global

  cat("g calling env: ")
  print(parent.frame()) #  where called (inside f) 

}

f <- function() {
  cat("f: nframe = ", sys.nframe() , "\n")
  cat("f def env:  ")
  print(environment(f))

  cat("f active env:  ")
  print(environment())
  cat("\n")
  g()
}
cat("nframe = ", sys.nframe() , "\n") # 0
f()
cat("nframe = ", sys.nframe() , "\n")

```

### NEED?
```{r}
# objects in parent.frame (calling env)
parentls <- function() {
  ls(envir = parent.frame())
}

a<-function() {
    x <- 5
    parentls()
}

b <- function() {
    z <- 10
    parentls()
 }

a() # objects in a's environment
b()
parentls()
```


AAA Example:   objects in calling env() (or parent.frame())
https://stackoverflow.com/questions/28641395/what-is-parent-frame-of-r
```{r}
# objects in parent.frame (calling env)
parentls <- function() {
  ls(envir = parent.frame())
}

a<-function() {
    x <- 5
    parentls()
}

b <- function() {
    z <- 10
    parentls()
 }

a() # objects in a's environment
b()
parentls()
```

AAA How many levels down ?  0=GlobalEnv
```{r nframe}
parentls <- function() {
  cat("nframe = ", sys.nframe() , "\n")
}


a  <- function() {
  cat("nframe = ", sys.nframe() , "\n")
  b()
}

b   <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
  c()
}

c  <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
}


cat("nframe = ", sys.nframe() , "\n")
a() # objects in a's environment

f  <- function() a()
f()
```
recursive!
sys.nframe()
```{r loop, eval=FALSE   }
a  <- function() {
  if (sys.nframe() == 9) return()
  cat("nframe = ", sys.nframe() , "\n")
  a()
}
a()
knitr::knit_exit()
```


