--- 
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document: 
    latex_engine: xelatex
    toc: TRUE 
    toc_depth:  4 
fontsize: 10pt 
geometry: margin=0.5in,top=0.25in 
TAGS:  env, frame
---

\small 

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)


## default option
options(error = NULL)
if (file.exists("testdump.rda")) file.remove("testdump.rda")
```

### Notes on exists()
    # must use quote(x)
    # exists has 3 ways to specifiy env: where, envir, frame=sys.frame(where)
    # note:  inherit=T by default

    # see note above
    # if (exists("x", envir = sys.frame())) print(x)
    # sapply( 0:3, function(x){ls(envir = sys.frame(x))} )

#### EXAMPLE:   show execution environment is same as env for frame number sys.frame(sys.nframe())  (here nframe=1)
```{r even_simpler}

f  <- function() {
    browser()
    x  <- "hi"
    identical(environment(), sys.frame(sys.nframe()))
}

f()
```

#### EXAMPLE:  probe execution environments for f and then g
  * manually confirm sys.* functions make sense.
  * once browser begins, debug(g) will be certain to show g
```{r f_g}

debug(g)

g  <- function() {
    y = "bye" 
}

f  <- function() {
      x  <- "hi"
      g()
}

f()

options(error = NULL)



#### Simplest:  do you understand?
```{r zero}
f  <- function() {
    x <- "hi"
    stop("testdump frames")
}

f()
list.files()
options(error = NULL)
```

#### dump.frames - 1 of 2
  *  copied from https://rdrr.io/r/utils/debugger.html
  *  env are not same
```{r dump.frames}
options(keep.source=T)

## choose ONE
options(error = recover)
# options(error = quote(dump.frames("testdump", TRUE)))

f <- function() {
    g <- function() stop("test dump.frames")
    g()
}
f()   # will generate a dump on file "testdump.rda"
options(error = NULL)
```

#### load, debugger  - restart R - 2 of 2
```{r debugger}
load("testdump.rda")
debugger(testdump)
```


#### EXAMPLE:  Add a branch?
```{r branch}
main  <- function() {
    f  <- function(x) {
        print("inside f")
        g(x) 
        h()
    }
    g  <- function(x) { 
    print("inside g")
    browser()
    x  <- 2
    }

    h  <- function() {
        x  <- 1
        "bye"
    }
    f()

}
main()
```



#### Ex 1: parent.frame? Use parent.frame to find objects in calling env. 
  *  Example 1
  *  https://stackoverflow.com/questions/28641395/what-is-parent-frame-of-r/28641459#28641459
```{r parent.frame}
##  Whenever parentls is called, ls reports back about calling environment.
##  For parent.frame(n), default value of n is 1.

parentls <- function(n) {
  ls(envir=parent.frame(n))
  # ls(envir=sys.frame(which=-2))   # also works!, but I have coded to use `n`.
}

## Since default of n = 1 in parent.frame, ls reports on  .Globalenv
parentls()

## use `index` to separate from `n`
a<-function(index=NULL) {
    x <- 5
    parentls(index)
}

b <- function() {
    z <- 10
    parentls()
 }

## Fails because not allowed to see inside sys.
a(index=0)

a(index=1)
# [1] "index" "x"    


a(index=2)  # grandparent, no index, no n 
# [1] "a"        "b"        "jim_lib"  "parentls"

b()  # use defaults(n=1)
# [1] "z"

```

#### Ex2: Move Up a Frame  
  *  Using debugger (follow discussion in !so)
  *  https://stackoverflow.com/questions/9796843/move-up-a-frame-debug-r-environment

```{r move_up}
{
f <- function() {
   
   x <-1
   g(x+1)
}
g <- function(z) {
  # browser()
   y = z+2
   return(y)
}
}
f()
```

#### Ex3: Logging without an error
https://stackoverflow.com/questions/64698732/how-to-show-stack-trace-without-error-in-r

```{r logging}
show_stack <- function() {
  cat("#----- Stack containing call to show_stack -----#\n\n")
  x <- sys.calls()
  browser()
  lapply(head(x, -1), function(x) {print(x); cat("\n")})
  cat("#-----------------------------------------------#\n\n")
}

#  Which you just insert in whichever function you want to trace:

f <- function() g()
g   <- function() h()
h <- function() show_stack()

f()
```

#### Ex4:   Show n= and which= -   can be equivalent
  *     (from sys.parent help) Notice that even though the sys.xxx functions (except sys.status) are
    interpreted, their contexts are not counted nor are they reported. There
    is no access to them. 
  *  "Non-negative values of which are frame numbers starting from .GlobalEnv
    whereas negative values are counted back from the frame number of the
    current evaluation."
```{r equal}

f <- function() g()
g   <- function() h()
h <- function() browser() #sys.call(which) 

debugonce(h)
f()


begin  <- function(e) {
    which <<- e
    f()
}
sapply(c(0, 1,2,3,4,5,6), begin)  # which > 0
sapply(c(0, -1, -2), begin)   # which <0
```

#### EX 5:  from ?sys.function
```{r}
     require(utils)
     
     ## Note: the first two examples will give different results
     ## if run by example().
     ff <- function(x) gg(x)
     gg <- function(y) sys.status()
     str(ff(1))
     
     gg <- function(y) {
         ggg <- function() {
             cat("current frame is", sys.nframe(), "\n")
             cat("parents are", sys.parents(), "\n")
             print(sys.function(0)) # ggg
             print(sys.function(2)) # gg
         }
         if(y > 0) gg(y-1) else ggg()
     }
     gg(3)
     
     t1 <- function() {
       aa <- "here"
       t2 <- function() {
         ## in frame 2 here
         cat("current frame is", sys.nframe(), "\n")
         str(sys.calls()) ## list with two components t1() and t2()
         cat("parents are frame numbers", sys.parents(), "\n") ## 0 1
         print(ls(envir = sys.frame(-1))) ## [1] "aa" "t2"
         invisible()
       }
       t2()
     }
     t1()
     
     test.sys.on.exit <- function() {
       on.exit(print(1))
       ex <- sys.on.exit()
       str(ex)
       cat("exiting...\n")
     }
     test.sys.on.exit()
     ## gives 'language print(1)', prints 1 on exit
     
     ## An example where the parent is not the next frame up the stack
     ## since method dispatch uses a frame.
     as.double.foo <- function(x)
     {
         str(sys.calls())
         print(sys.frames())
         print(sys.parents())
         print(sys.frame(-1)); print(parent.frame())
         x
     }
     t2 <- function(x) as.double(x)
     a <- structure(pi, class = "foo")
     t2(a)
     
###
```

#### trace   - not working
```{r simple_trace}
main  <- function() {
    x  <- "hi"
    stop("trouble")
}

trace(what = main(), 
      tracer = browser())

untrace(what = main)
```


#### Adv-R, Cube vs Square, Chapter 10, 11
  *  Show, identical body
  *  Difference is function environment
```{r cube}
```

#### helpers
```{r}

bug_fun<-function(generations_back, envir=globalenv())
{
	print(parent.frame(generations_back))
	
	print(sys.frame(sys.parent(generations_back)))
}

bug_fun(n=1)
```


#### bquote another way to get value in another frame???
```{r bquote}
#  bquote(expr, where = parent.frame(), splice = FALSE)
f  <- function() {
    x  <- 1
    g()
}

g  <- function() {
      x  <- 2
      browser()
}

## in browser, use quote(.(x), where=parent.frame()) 1
## in browser, use quote(.(x), where=environment() or where=sys.frame(2)) 2
f()

```
```{r render, eval=F, include=F}
output_dir  <- Sys.getenv("OUTPUT_DIR")
output_dir

{
file  <-"/home/jim/code/r_environment_code/015_env_puzzles_examples.Rmd"  

## dislike `here`?

## get dir/file name separately, then combine
 the_dir  <- dirname(file)
 the_dir
 file  <- basename(file)
 file
 file  <- file.path(the_dir, file)
 file

#   file  <- here("rmd", file)
file
}

### DO NOT KNIT !
### too many environment levels; 
### DO NOT KNIT !
# rmarkdown::render(file,
                #  output_format="html_document",
                  output_format="pdf_document",
                  output_dir=output_dir
                  )
```

	 vim:linebreak:nowrap:nospell:cul tw=78 fo=tqlnr foldcolumn=3 
