
---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bbm}
  - \usepackage{threeparttable}
  - \usepackage{forest}
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
#       extra_dependencies: ["amssymb", "bbm", "threeparttable", "forest"]
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  4 
    extra_dependencies: ["amssymb", "bbm", "threeparttable", "forest"]
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS:  math, latex, trees, forest
---

<!--  
as of August 2021
-PDF works
-HTML does NOT work
-->


### How many levels down ?  

  -  0=GlobalEnv  
  -  chain of functions, a() calls b() ...  
```{r nframe_levels}

a  <- function() {
  cat("nframe = ", sys.nframe() , "\n")
  b()
}

b   <- function(){ 
  cat("nframe = ", sys.nframe() , "\n")
  print(paste0("Called from ", sys.call()))
  c()
}

c  <- function() {
  cat("nframe = ", sys.nframe(), "\n")
  print(paste0("Called from ", sys.call()))
  #cat("called from ", sys.call(), "\n")
  #sys.calls()
}

cat("nframe = ", sys.nframe(), "\n")

f  <- function() a()
f()
```

#### Embed `modified` latex equations inside Rmd; compile with knitr
Seems to work Great (pdf:  even installs needed latex packages )


#### Latex:  draw nframes

\begin{forest}
  for tree={
    fit=band,% spaces the tree out a little to avoid collisions
  }
  [.GlobalEnv
    [nframe=1, tier=vegetables
      ["nframe=2", tier=fruits]
    ]
  ]
\end{forest}

#### Latex:  draw trees
\begin{forest}
  for tree={
    fit=band,% spaces the tree out a little to avoid collisions
  }
  [things
    [cabbages, tier=vegetables
      [peaches, tier=fruits]
    ]
    [kings, tier=aristocrats]
    [sealing wax
      [queens, tier=aristocrats
        [carrots, tier=vegetables]
        [pineapple, tier=fruits]
        [aubergine, tier=vegetables]
      ]
    ]
  ]
\end{forest}


```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = T   ) # easier to read
```



#### Raw latex
  *  REF:  rmarkdown-cookbook, pandoc will leave as latex
```{=latex}
\begin{tabular}{ll}
A & B \\
A & B \\
\end{tabular}
```

```{r render, eval=FALSE, include=FALSE 	} 
# !zathura ~/Downloads/print_and_delete/ 
# for debugging

options(tinytex.verbose = TRUE)

{
  file <- "0410_latex_trees.Rmd"
  #file  <- file.path(paste0("~/code/publish_project/MATH/", file))
  #file  <- here("MATH", file)
  file  
}

# NOTE:   .tex only works with PDF
# NOTE:    tex will NOT work with html
# in general, pdf will look nicer

output_dir= Sys.getenv("OUTPUT_DIR")
output_dir
rmarkdown::render(file,
                  output_format = "pdf_document"
                  #output_format = "html_document",
                  #output_dir = output_dir
)
```
